\documentclass{article}
\usepackage[ruled,linesnumbered,lined]{algorithm2e}
\usepackage[braket]{qcircuit}
\usepackage[final]{listings}
\usepackage{caption,subcaption}
\usepackage{graphicx}
\usepackage[margin=3cm]{geometry}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}

\lstset{numbers=left, numberstyle=\tiny, stepnumber=2, numbersep=5pt,
basicstyle=\small, stringstyle=\ttfamily, showstringspaces=false}

\title{}
\author{}

\begin{document}
\maketitle
\begin{abstract}
  A probabilistic quantum memory is the quantum equivalent of a 
  content-addressable associative memory. It is capable of storing and 
  recovering large amounts of information using quantum superposition. 
  Probabilistic quantum memories can be used as quantum classifiers in quantum 
  machine learning algorithms. The main limitation of this probabilistic 
  quantum memory is the necessity to measure the memory in order to recover 
  information; the measurement breaks the quantum system and the information 
  must be reinserted on the memory. However, some applications with just a 
  single shot of the recovering algorithm and the application of the quantum 
  probabilistic memory can lead to super-polynomial advances in heuristic 
  search when a maximum value is known.
  
  In this work we propose a modified version of a probabilistic quantum memory 
  that uses a scale parameter $\phi$. 
  
  In this work we propose a modified version of a probabilistic quantum memory, 
  model able to store and recover information using quantum superposition.  
  However, some applications with just a single shot of the recovering 
  algorithm and the application of the quantum probabilistic memory can lead to 
  super-polynomial advances in heuristic search when a maximum value is known. 
  A simple quantum classifier can be devised by using a set of quantum memories 
  storing training patterns (...). 
  
  In this work, we propose a modified version of a probabilistic quantum 
  memory, which is able to improve its classification accuracy through the 
  inclusion of a scale parameter.
  
  We create a classical/quantum protocol to implemented the memory on a real 
  quantum device using a five bit quantum computer.. Through classical 
  experimentation we evaluated the influence of the scale parameter on the 
  pattern classification capabilities of the memory. The proposed parametric 
  quantum probabilistic memory allow the adjustment of the quantum memory to a 
  given task. Hence, it can better suit the task of machine learning model 
  evaluation, once we can adjust the scale parameter to improve the 
  classification accuracy. 
\end{abstract}

\bibliographystyle{unsrt}
\bibliography{bibliografia}

\end{document}
